---
title: "Mediation Stress ISEL "
author: "Tracy Darbeloff"
date: "4/26/2018"
bibliography: "sample.bib"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(car)
library(ggplot2)
library(haven)
library(jtools)
library(stats)
library(ggpubr)
library(dbplyr)
library(lm.beta)
library(investr)
library(MASS)
library(lmSupport)
library(caret)
source("ISEL_descriptives.R")
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
```
testing for git
$R^2$
$\beta$

The data was box cox transformed due to a severe positive skew (*p*=`r shapiro_test_results$p.value`).

We did this cool thing that someone did [@kim2018link].

Create ratio score for ERQ use of regulation techniques and MASQ timepoints 
```{r timepoints}
d$ERQ_Tend <- d$ERQ_Reap/d$ERQ_Sup
d$ERQ_Tend_log <- log(d$ERQ_Tend)
d$ERQtend_z <- scale(d$ERQ_Tend_log)[,1]

fit1 <- lm(MASQtot_T3 ~ MASQTot_T1, d) %>% tidy()
d$Resid_MASQ <- fit1$residuals

```

``` {r pvals}
fit1_pval <- ifelse(fit1$p.value[2]<.001,"*p*<.001","*p*=fit1$p.value[2]")
```
MASQ at time point one and timepoint two were significantly correlated (*b* = `r fit1$estimate[2]`, `r fit1_pval`).

```{r histMASQ}
hist(d$MASQTot_T1)
```


Check gender differences
```{r gendiff}
d$Sex_rc <- recode(d$Sex, "1 = '1'; 2 = '0'")

d$Sex_fac <- factor(d$Sex_rc, levels = c("0", "1"))

d$ISEL_c <- d$ISEL - mean(d$ISEL)
d$ERQRep_c <- d$ERQ_Reap - mean(d$ERQ_Reap)
d$ERQSup_c <- d$ERQ_Sup - mean(d$ERQ_Sup)
d$MASQtot_T3_c <- d$MASQtot_T3 - mean(d$MASQtot_T3)
d$MASQTot_T1_c <- d$MASQTot_T1 - mean(d$MASQTot_T1)
d$ERQ_Tend_c <- d$ERQ_Tend - mean(d$ERQ_Tend)

ERQRep_Gen <- lm(ERQRep_c ~ Sex_fac, d)
summary(ERQRep_Gen)

ERQSup_Gen <- lm(ERQSup_c ~ Sex_fac, d)
summary(ERQSup_Gen)

ERQTend_Gen <- lm(ERQ_Tend_c ~ Sex_fac, d)
summary(ERQTend_Gen)

MASQT1_Gen <- lm(MASQTot_T1_c ~ Sex_fac, d)
summary(MASQT1_Gen)

MASQT3_Gen <- lm(MASQtot_T3_c ~ Sex_fac, d)
summary(MASQT3_Gen)

ISEL_Gen <- lm(ISEL_c ~ Sex_fac, d)
summary(ISEL_Gen)
```



check if emotion regulation tendencies are correlated with future changes in depression and anxiety symptoms (path C)
```{r path c and c`}
summary(lm(Resid_MASQ ~ ERQtend_z, d))
summ(lm(MASQtot_T3z ~ ERQtend_z+ MASQTot_T1z, d))

PathMed <- lm(MASQtot_T3z ~ ISEL_z + ERQtend_z + MASQTot_T1z + Sex + Age + AnyDx, d)
summary(PathMed)
```

It is not. But that isn't the end of the world. Path C does not need to be significant.

Path A (ERQ tendency (pos = use reappraisal) correlated with ISEL)
```{r path A}
PathA <- lm(ISEL_z ~ ERQtend_z + Age + Sex + AnyDx, d)
summary(PathA)
```

Path B (ISEL predicting changes in MASQ)
```{r Path B}
PathB <- lm(MASQtot_T3z ~ ISEL_z + MASQTot_T1z + Age + Sex + AnyDx, d)
summary(PathB)

```


Path A for Reappraisal and Suppression separately
```{r path A sep}
PathA_rep <- lm(ISEL_z ~ ERQRep_z*Sex_fac + Age + AnyDx, d)
summary(PathA_rep)

PathA_sup <- lm(ISEL_z ~ ERQSup_z*Sex_fac + Age + AnyDx, d)
summary(PathA_sup)
```



Let's split by gender
```{r gen}
d_fem <- subset(d, Sex_fac == 0)
d_male <- subset(d, Sex_fac==1)
```


Lets look at women vs Men with reappraisal
```{r reap women}

FemRep_A <- lm(ISEL_z ~ ERQRep_z + Age + AnyDx, d_fem)
summary(FemRep_A)
MaleRep_A <- lm(ISEL_z ~ ERQRep_z + Age + AnyDx, d_male)
summary(MaleRep_A)



Fem_B <- lm( MASQtot_T3z ~ ISEL_z + MASQTot_T1z + Age + AnyDx, d_fem)
summary(Fem_B)
Male_B <- lm( MASQtot_T3z ~ ISEL_z + MASQTot_T1z + Age + AnyDx, d_male)
summary(Male_B)
```

Lets look at women vs men with suppression
```{r sup women}

FemSup_A <- lm(ISEL_z ~ ERQSup_z + Age + AnyDx, d_fem)
summary(FemSup_A)
MaleSup_A <- lm(ISEL_z ~ ERQSup_z + Age + AnyDx, d_male)
summary(MaleSup_A)


summary(Fem_B)
summary(Male_B)
```





Split by Dx, see any changes?
```{r Dx}
d_dx <- subset(d, AnyDx==1)
dx_c <- lm(MASQtot_T3z ~ ERQRep_z + MASQTot_T1z + Sex + Age, d_dx)
summary(dx_c)
dx_a <- lm(ISEL_z ~ ERQRep_z + Sex + Age, d_dx)
summary(dx_a)
dx_med <- lm(MASQtot_T3z ~ ISEL_z + MASQTot_T1z+ Sex_fac + Age, d_dx)
summary(dx_med)
```


Find individual variances
```{r resid variance}
reg <- lm(MASQtot_T3z ~ MASQTot_T1z + Age, d)
d$Resid_Var <- reg$residuals
hist(d$Resid_Var)

Reap <- lm(Resid_Var ~ ERQRep_z + Sex, d)
summary(Reap)

Sup <- lm(Resid_Var ~ ERQSup_z + Sex, d)
summary(Sup)

Isel <- lm(Resid_Var~ ISEL_z + Sex, d)
summary(Isel)
```




